MWA tied-array processing III: Microsecond time resolution via a synthesis filter

### 2019-10-22 ipfb.tex
Improved the filter analysis plot

The first stage (coarse) PFB is described in \citet{Prabu2015}, and here we only document a few details pertaining to the second stage (fine) PFB.
A PFB is completely specified by (1) the number of output channels, $N$, (2) the number of taps, $P$, and (3) the analysis filter, $h[m]$, $0 \le m < M=NP$.
For the MWA, $N=128$ (giving fine channels $10\,$kHz wide), $P=12$, and
\begin{equation}
    h[m] = w_H[m]\,w_s[m],
    \label{eqn:filter}
\end{equation}
where
\begin{equation*}
    w_H[m] = \sin^2\bigg(\frac{\pi (m+1)}{M+1}\bigg)
\end{equation*}
is the Hanning window, and
\begin{equation*}
    w_s[m] = \sinc\bigg(\frac{\pi(m + 1 - M/2)}{N}\bigg)
\end{equation*}
is the scaled $\sinc(x) = \sin(x)/x$ function.
It can be easily checked that $h[m]$ is defined to be symmetric around sample $m = 767 = M/2-1$.
The analysis filter is shown in Fig. \ref{fig:filter}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{filter}
    \caption{The coefficients of the analysis filter defined in Eq. \eqref{eqn:filter}, composed of a Hanning window multiplied to a $\sinc$ function.}
    \label{fig:filter}
\end{figure}

>>>>

The first stage (coarse) PFB is described in \citet{Prabu2015}, and here we only document a few details pertaining to the second stage (fine) PFB.
A PFB is completely specified by (1) the number of output channels, $N$, (2) the number of taps, $P$, and (3) the analysis filter, $h[m]$, $0 \le m < M=NP$.
For the MWA, $N=128$ (giving fine channels $10\,$kHz wide), $P=12$, and
\begin{equation}
    h[m] = w_H[m]\,w_s[m],
    \label{eqn:filter}
\end{equation}
where
\begin{equation*}
    w_H[m] = \sin^2\bigg(\frac{\pi (m+1)}{M+1}\bigg)
\end{equation*}
is the Hanning window, and
\begin{equation*}
    w_s[m] = \sinc\bigg(\frac{\pi(m + 1 - M/2)}{N}\bigg)
\end{equation*}
is the scaled $\sinc(x) = \sin(x)/x$ function.
It can be easily checked that $h[m]$ is defined to be symmetric around sample $m = 767 = M/2-1$.
The analysis filter is shown in Fig. \ref{fig:filter}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{filter}
    \caption{Top: The coefficients of the analysis filter defined in Eq. \eqref{eqn:filter}, composed of a Hanning window multiplied to a $\sinc$ function. Bottom: The frequency response of the analysis filter, showing negligible attenuation across approximately $10\,$kHz (the bandwidth of a fine channel) and strong attenuation elsewhere.}
    \label{fig:filter}
\end{figure}
